---
title: "STA6235 Week 3"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

## Tuesday, September 5

1. From last week: pull in the [Palmer penguins dataset](https://allisonhorst.github.io/palmerpenguins/).

```{r}

```

2. From last week: model penguin body mass (*body_mass_g*) as a function of flipper length (*flipper_length_mm*) and bill length (*bill_length_mm*). Remember to state the resulting regression model.

```{r}

```

3. Find the $R^2$ and $R^2_{\text{adj}}$ for the model.

```{r}

```

4. Provide a brief interpretation of the $R^2_{\text{adj}}$ value.

5. Explain the model assumptions in your own words.

6. Assess the model assumptions using the graphical method shown in class. Does our model meet the assumptions necessary for statistical inference?

```{r}

```

7. Check for outliers. How many exist? 

```{r}

```

8. Check influence and leverage - are there any points we need to check? Which ones?

```{r}

```

9. Check multicollinearity - are there any issues with our model?

```{r}

```

## Thursday, September 7

10. Create indicator variables for the species of penguin (*species*).

```{r}

```

11. Model penguin body mass (*body_mass_g*) as a function of flipper length (*flipper_length_mm*), bill length (*bill_length_mm*), and the species (*species*). Remember to state the resulting regression model. 

```{r}

```

12. Use the appropriate hypothesis test to determine if this is a significant regression line. Test at the $\alpha=0.05$ level. Remember to typeset your results.

```{r}

```

13. Use the appropriate hypothesis test(s) to determine which, if any, are significant predictors of penguin body mass. Test at the $\alpha=0.05$ level. Remember to typeset your results.

```{r}

```

14. Create a data visualization for your regression model. Create the regression line for each species.

```{r}

```

15. Now that we've introduced species to the model, do we still meet the model assumptions?

```{r}

```
















